### 2017-04-01 paper/evaluation.tex
organizing eval
pass on eval

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python 3.4, Bash, and R to process the data and generate plots.  All
source artifacts are publicly available (on request) for
replication\Comment{ at \Fix{create gh-pages}}.  This includes
supporting scripts (\eg, the script that test subjects and generates
the raw data), and the full list of projects. \Comment{, and a
  \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

\subsection{Answering research question \numRQA{}}
\label{sec:rqA}

\begin{itemize}
    \item \emph{\RQA}
\end{itemize}

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests. \Jbc{The following
steps may change $\rightarrow$}
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  To avoid noise from
operating system events, we used a dedicated server remotely via SSH
with the operating system running only essential services (\eg, the
SSH server). In addition, we configured the \CodeIn{isolcpus} option
from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
to execute our experiment and the remaining CPUs to run the operating
system. By isolating a set of virtual CPUs, we prevent
context-switching from experiment processes and OS-related processes.

@@

We ran each subject's tests three times and grouped them according to
the time cost (in average): tests that run in less than a minute
(\shortg{} group), tests than run in one minute and less than five
minutes (\medg{} group), and tests that run in five (or more) minutes
(\longg{} group). We based our classification from a previous work
\cite{gligoric-etal-issta2015} and added the \medg{} group due to the
variability of the time cost from subjects out of the \shortg{} group.
\Jbc{these results will be updated $\rightarrow$}
Figure~\ref{fig:rq1-boxplot} shows the time cost distribution of each
group: the \shortg{} group is the most right skewed distribution with
outliers closed to the \medg{} group and 50\% of the subjects run in
less than 15 seconds; the median from the \medg{} group is nearly two
minutes and most of the subjects run in less than four minutes; most
of the \longg{} group runs in less than 25 minutes but has outliers
that require more than 50 minutes to execute.
Figure~\ref{fig:rq1-barplot} summarizes the proportion of subjects
from each group.

@@

\subsection{Answering research question \numRQB{}}
\label{sec:rqB}

\begin{itemize}
    \item \emph{\RQB}
\end{itemize}

>>>>

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python 3.4, Bash, and R to process the data and generate plots.  All
source artifacts are publicly available for replication (on
request)\Comment{ at \Fix{create gh-pages}}.  This includes supporting
scripts (\eg, the script that test subjects and generates raw analysis
data) and the full list of projects. \Comment{, and a
  \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

\subsection{Potential}
\label{sec:rqA}
\label{sec:rqB}

\begin{itemize}
    \item \textbf{\RQA}
\end{itemize}

We considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
to evaluate prevalence of projects with costly test suites.  To
measure cost we used the following methodology. \Jbc{The following
  steps may change $\rightarrow$} Figure~\ref{fig:mvn-execution} shows
the commands used in our script to test each subject. The main loop
(lines 5-11) iterates over the list of subjects and invokes Maven at
different steps (lines 7-9) as to reduce measurement noise.  We first
compiled the source and test files (line 7), made all dependencies
available locally (line 8) and later, we ran the tests in offline mode
(line 9) to bypass package updates. After the execution, we used a
regular expression on the output log to extract the elapsed time (line
10).

Prior to running this script, we randomly selected a hundred projects
to inspect corresponding execution logs.  The goal of the inspection
was to identify tasks unrelated to testing (\eg, \emph{javadoc}
generation and static analysis) that could interfere in our
measurement.  These extra tasks were ignored from execution (lines
1-3).  Furthermore, to avoid noise from operating system events, we
configured our workstation to run only essential services.  The
machine was dedicated to our experiments and we accessed it via
SSH. In addition, we configured the \CodeIn{isolcpus} option from the
Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs to
execute our experiment and the remaining CPUs to run the operating
system. By isolating a set of virtual CPUs, we prevent
context-switching from experiment processes and OS-related
processes.\Mar{can we cite this?}

@@

We ran the test suite for each subject three times reporting their
averages.  We grouped measurements in three time ranges: tests that
run within a minute (\shortg{} group), tests that run in one to five
minutes (\medg{} group), and tests that run in five or more minutes
(\longg{} group). We based our classification from a previous work
\cite{gligoric-etal-issta2015} and added the \medg{} group due to the
variability of the time cost from subjects out of the \shortg{} group.
\Jbc{these results will be updated $\rightarrow$}
Figure~\ref{fig:rq1-boxplot} shows the time cost distribution of each
group: the \shortg{} group is the most right skewed distribution with
outliers closed to the \medg{} group and 50\% of the subjects run in
less than 15 seconds; the median from the \medg{} group is nearly two
minutes and most of the subjects run in less than four minutes; most
of the \longg{} group runs in less than 25 minutes but has outliers
that require more than 50 minutes to execute.
Figure~\ref{fig:rq1-barplot} summarizes the proportion of subjects
from each group.

@@

\vspace{1ex}
\begin{itemize}
    \item \textbf{\RQB}
\end{itemize}
